---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Introduction to TB Models

A shiny app reproducing the models used in the Introduction to Tuberculosis modelling course practicals, run by [TB MAC](http://tb-mac.org/) at the [2017 Union conference](http://guadalajara.worldlunghealth.org/about-us). See the [TB MAC](http://tb-mac.org/) website for course materials and further resources. The models used in this course, and reproduced in this shiny app, were based on one published by [Lin et al.](http://www.who.int/bulletin/volumes/90/10/11-101436.pdf)

## Installing the shiny app locally

## Manual Install

To install and run the shiny app locally on your own computer you will need to first install [R](https://www.r-project.org/), it is also suggested that you install [Rstudio](https://www.rstudio.com/products/rstudio/download/). After downloading the source code from [this repository](https://www.github.com/seabbs/intro_to_tb_models) click on the `intro_to_tb_models.Rprof` file, this will open an Rstudio window. Type the following code into the command line;

```{r, eval = FALSE}
install.packages("shiny")
install.packages("shinydashboard")
install.packages("DT")
install.packages("ggplot2")
install.packages("tidyr")
install.packages("dplyr")
install.packages("tibble")
install.packages("rmarkdown")
install.packages("plotly")
```

To run the app open the `ui.R` file and press run, depending on your computer this may take some time.


### Using Docker

[Docker](https://www.docker.com/what-docker) is a container software that seeks to eliminate "works on my machine" issues. For installation and set up instructions see [here](https://www.docker.com/community-edition). 

This docker container is based on the [shiny](https://hub.docker.com/r/rocker/shiny/) docker image, see [here](https://github.com/rocker-org/shiny) for instructions on use. To run the docker image run the following in a bash shell:

```{bash, eval = FALSE}
docker pull seabbs/intro_to_tb_models
docker run --rm -p 3838:3838 seabbs/intro_to_tb_models
```

The shiny app can be found on port `:3838` at your local machines ip (or localhost on windows).



